Declarative Deployment Reconfiguration of Pulverised Collective Adaptive Systems at Runtime \thanks{Identify applicable funding agency here. If none, delete this.}

### 2023-05-16 paper-2023-acsos-pulverization.tex
restructure the paper, write the background

\begin{abstract}
In recent years,
the infrastructure supporting the execution of situated distributed computations
evolved with a fast pace.
%
Modern collective adaptive applications -- as found in the Internet of Things, swarm robotics, and social computing -- are designed to be executed on very diverse devices
and to be deployed on infrastructures composed of devices ranging from cloud servers to wearable devices,
constituting together a cloud-edge continuum.
%
The availability of such an infrastructure opens to better resource utilisation and performance,
but, contextually, introduces new challenges to software designers,
as applications must be conceived to be able to adapt their deployment to changing conditions.
%
In this paper,
we introduce a practical framework for the development of collective adaptive systems
based on the concept of \emph{pulverisation},
meant to neatly separate business logic and deployment concerns,
allowing applications to be defined independent of the infrastructure they will execute upon.
%
The framework is based on a domain-specific language capturing,
in a declarative fashion,
pulverised application components, device capabilities, resource allocation, and (runtime re-) configuration policies.
%
The framework, implemented in Kotlin multiplatform and available as open source,
is then evaluated in a small-scale real-world demo and in a city-scale simulated scenario.
\end{abstract}

>>>>

\begin{abstract}
In recent years,
the infrastructure supporting the execution of situated distributed computations
evolved with a fast pace.
%
Modern collective adaptive applications are designed to be executed on very diverse devices
and to be deployed on infrastructures composed of devices ranging from cloud servers to wearable devices,
constituting together a cloud-edge continuum.
%
The availability of such an infrastructure opens to better resource utilisation and performance,
but, contextually, introduces new challenges to software designers,
as applications must be conceived to be able to adapt their deployment to changing conditions.
%
In this paper,
we introduce a practical framework for the development of collective adaptive systems
based on the concept of \emph{pulverisation},
meant to neatly separate business logic and deployment concerns,
allowing applications to be defined independent of the infrastructure they will execute upon.
%
The framework is based on a domain-specific language capturing,
in a declarative fashion,
pulverised application components, device capabilities, resource allocation, and (runtime re-) configuration policies.
%
The framework, implemented in Kotlin multiplatform and available as open source,
is then evaluated in a small-scale real-world demo and in a city-scale simulated scenario.
\end{abstract}
